A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-08 main.tex
Wrote a paragraph of Multistage Programming with Dependent Types

Although unrolled \verb|add| function is optimzied, we cannot use it for different vector length.
For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
This problem is serious but existing type systems for multistage calculi cannot prevent it.

@@

\subsubsection{依存型とは何か?}

Dependent types are types which is dependent on values.
For example, we can realize vectors with their sizes with them.

\subsubsection{依存型のメリットをサイズ付きのvector, matrixの例を用いて説明する}

The merit of dependent types is guarantee of properties of programs more precisely.

\subsection{Multistage Programming with Dependent Types}

\subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}

We resolve Specialized Code Problem using dependent types.

>>>>

Although unrolled \verb|add| function is optimzied, we cannot use it for different vector length.
For example, when you optimize for the length of 5, you shoudn't use it for vectors of 3 lengths.
Otherwise, we will get Segmentation Fault error.
This problem is serious but existing type systems for multistage calculi cannot prevent it.

@@

% \subsubsection{依存型とは何か?}

Dependent types are types which is dependent on values.
We can use dependent types for securer programming than ordinary types.
For example, we can realize vectors with their sizes with them.
\begin{verbatim}
        Vector :: Int -> *
\end{verbatim}
\verb|Vector| is a type constor which takes the length of vectors.
\verb|Vector 3| is a type for vectors whose lengths are 3.
We can confirm the arguments of \verb|add| function is the same with dependent types.
\red{secure programming? finer grained typing? とか}

\subsection{Multistage Programming with Dependent Types}
\red{このsectionは短いので上とくっつけてもいいかもしれない}

% \subsubsection{「生成した行列計算のコードは特定のサイズに特化しており、他のサイズでは使えない。
% このため、間違って組み合わせると容易にエラーを引き起こす。」問題を依存型で解決する。}

As above, functions generated with multistage programming can take more restricted values as arguments.
When you optimize \verb|add| function for the length of 5, you should it only for 5 length vectors.
We introduce dependent types into a multistage calculus
so that the type sysytem can guarantee optimzied functions are used properly.
